On exponential sums arising from the classical doubling method

### 2025-04-09 main.tex
Removing dual group Frobenius

The \emph{dual group over $\finiteField$} of $\algebraicGroup{G}$ with respect to the torus $\algebraicGroup{T}$ corresponds to the group $\algebraicGroup{G}^*$ with a dual torus $\algebraicGroup{T}^*$ and root datum
\[
(\CharacterLattice{\algebraicGroup{T}^*},\Phi_{\algebraicGroup{T}^*},\CocharacterLattice{\algebraicGroup{T}^*},\Phi_{\algebraicGroup{T}^*}^\vee) \cong (\CocharacterLattice{\algebraicGroup{T}},\Phi_{\algebraicGroup{T}}^\vee,\CharacterLattice{\algebraicGroup{T}},\Phi_{\algebraicGroup{T}})
\]
such that the isomorphism respects the Frobenius actions on $\CharacterLattice{\cdot}$ and $\CocharacterLattice{\cdot}$.

@@

We will need the following facts about Lusztig series.

The first fact tells us that Lusztig series of $\GroupExtension{\algebraicGroup{G}}$ are unions of Harish-Chandra series, and establishes a relation between the corresponding semisimple conjugacy classes.
\begin{proposition}[{\cite[Proof of Corollary 3.3.21]{GeckMalle2020}}]\label{prop:lusztig-series-are-unions-of-harish-chandra-series}
	For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ is a union of Harrish--Chandra series corresponding to Harrish-Chandra data of the form $\left(\FrobeniusFixedPoints{\algebraicGroup{P}},\sigma\right)$ where $\algebraicGroup{P}$ is a parabolic subgroup of $\algebraicGroup{\GroupExtension{G}}$ with Levi part $\algebraicGroup{L}$ with $s \in \DualFrobeniusFixedPoints{L}$ and $\sigma \in \LusztigSeries{\FrobeniusFixedPoints{L}}{s}$ is an irreducible cuspidal representation.
\end{proposition}

The next fact establishes a relation between the Lusztig series of $\GroupExtension{\algebraicGroup{G}}$ and of $\algebraicGroup{G}$.
\elad{Explain $i^{\ast}$}\elad{Should we deprecate the notation $\Frobenius^{\ast}$?}

\begin{proposition}[{\cite[Proposition 11.7]{Bonnafe2006}}]\label{prop:lusztig-series-and-restriction}
	Let $\tilde{s}$ be a semisimple element of $\DualFrobeniusFixedPoints{\GroupExtension{G}}$ and let $s = i^{\ast}\left(\tilde{s}\right)$. Then
	\begin{enumerate}
		\item If $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ and if $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $\FrobeniusFixedPoints{G}$, then $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$.
		\item Let $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$. Then there exists $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ such that $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $\FrobeniusFixedPoints{G}$.
	\end{enumerate}
\end{proposition}

@@

\begin{proposition}[{\cite[Page 172]{Lusztig1977}}]\label{prop:at-most-one-cuspidal-lusztig-series}
	For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ contains at most one cuspidal element.
\end{proposition}

>>>>

The \emph{dual group over $\finiteField$} of $\algebraicGroup{G}$ with respect to the torus $\algebraicGroup{T}$ corresponds to the group $\algebraicGroup{G}^*$ with a dual torus $\algebraicGroup{T}^*$ and root datum
\[
(\CharacterLattice{\algebraicGroup{T}^*},\Phi_{\algebraicGroup{T}^*},\CocharacterLattice{\algebraicGroup{T}^*},\Phi_{\algebraicGroup{T}^*}^\vee) \cong (\CocharacterLattice{\algebraicGroup{T}},\Phi_{\algebraicGroup{T}}^\vee,\CharacterLattice{\algebraicGroup{T}},\Phi_{\algebraicGroup{T}})
\]
such that the isomorphism respects the Frobenius actions on $\CharacterLattice{\cdot}$ and $\CocharacterLattice{\cdot}$. Some authors distinguish the Frobenius actions on $\algebraicGroup{G}$ and $\algebraicGroup{G}^{\ast}$ by writing $\Frobenius$ and $\Frobenius^{\ast}$, respectively, but we will not do so and simply denote both actions by $\Frobenius$.

@@

Let us specialize to the classical groups $\algebraicGroup{G}$ and their extensions $\GroupExtension{\algebraicGroup{G}}$ from Sections \ref{subsec:isometry-groups} and \ref{subsec:similitute-groups}. We will need the following facts about Lusztig series of $\algebraicGroup{G}$ and $\GroupExtension{\algebraicGroup{G}}$.

The first fact tells us that Lusztig series of $\GroupExtension{\algebraicGroup{G}}$ are unions of Harish-Chandra series, and establishes a relation between the corresponding semisimple conjugacy classes.
\begin{proposition}[{\cite[Proof of Corollary 3.3.21]{GeckMalle2020}}]\label{prop:lusztig-series-are-unions-of-harish-chandra-series}
	For any semisimple element $s \in \FrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ is a union of Harrish--Chandra series corresponding to Harrish-Chandra data of the form $\left(\FrobeniusFixedPoints{\algebraicGroup{P}},\sigma\right)$ where $\algebraicGroup{P}$ is a parabolic subgroup of $\algebraicGroup{\GroupExtension{G}}$ with Levi part $\algebraicGroup{L}$ with $s \in \FrobeniusFixedPoints{L}$ and $\sigma \in \LusztigSeries{\FrobeniusFixedPoints{L}}{s}$ is an irreducible cuspidal representation.
\end{proposition}

The next fact establishes a relation between the Lusztig series of $\GroupExtension{\algebraicGroup{G}}$ and of $\algebraicGroup{G}$.
\elad{Explain $i^{\ast}$}

\begin{proposition}[{\cite[Proposition 11.7]{Bonnafe2006}}]\label{prop:lusztig-series-and-restriction}
	Let $\tilde{s}$ be a semisimple element of $\FrobeniusFixedPoints{\GroupExtension{G}}$ and let $s = i^{\ast}\left(\tilde{s}\right)$. Then
	\begin{enumerate}
		\item If $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ and if $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $\FrobeniusFixedPoints{G}$, then $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$.
		\item Let $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$. Then there exists $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ such that $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $\FrobeniusFixedPoints{G}$.
	\end{enumerate}
\end{proposition}

@@

\begin{proposition}[{\cite[Page 172]{Lusztig1977}}]\label{prop:at-most-one-cuspidal-lusztig-series}
	For any semisimple element $s \in \FrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ contains at most one cuspidal element.
\end{proposition}
